My Cool Title

### 2019-05-05 paper.tex
Removed table of items per room and put it in normal list

The environment, and the object placement within it, for both experiments was modelled on a typical office.
Measures were taken to ensure that both office environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
All of the objects and their experiment placement is given in Table~\ref{tab:objects}.

\begin{table}
  \centering
  \caption{The different objects used within each experiment environment.}\label{tab:objects}
  \begin{tabular}{p{2cm}cp{0.7cm}c}
    \toprule
    & \bf{Guided} & & \bf{Unguided} \\\midrule
    Door        & X & & X \\\midrule
    Desk	& X & & X \\\midrule
    Chair	& X & & X \\\midrule
    Whiteboard	& X & & X \\\midrule
    Mouse	& X & & X \\\midrule
    Monitor	&   & & X \\\midrule
    Telephone	&   & & X \\\midrule
    Keyboard	&   & & X \\\midrule
    Laptop	& X & &   \\\midrule
    Backpack	& X & &   \\\midrule
    Mug		& X & &   \\\midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ dimensions.
By integrating these data with respect to time, we can get the total displacement for each dimension.

>>>>

The environment, and the object placement within it, for both experiments was modelled on a typical office.
Measures were taken to ensure that both office environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
The objects in the guided experiment environment is

\begin{equation}
  z_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
\end{equation}
while the objects in the unguided experiment are

\begin{equation}
  z_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
\end{equation}
A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.

@@

The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ (tilt) dimensions.
By integrating these data with respect to time, we can get the total displacement for each dimension.
